\section{Related Work}
This section describes related work of shuffle optimization.

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce \cite{hadoop} is the most classic approach to handle shuffle overhead. Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, map and reduce slot ratio, etc). DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage to decrease the time of waiting for outputs of map tasks. All of them left the explicit I/O time in an occupied computation slot. Instead, SCache can start shuffle pre-fetching without consuming slots. iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages, in order to start fetching data from previous stage earlier. But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing by combining DAG information and heuristic algorithms.

\textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when network is saturated. At the same time, it achieves better data locality. Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. But all of them can not mitigate explicit I/O in both map and reduce tasks. In addition their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle in-memory caching and pre-fetching.

\textbf{Network layer optimization}: Varys \cite{varys} and Aalo \cite{aalo} provide the network layer optimization for shuffle transfer. Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.